---
title: "Journal (reproducible report)"
author: "Julius Häuslein"
date: "2020-11-23"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    toc_depth: 3
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```


# Bike Sales

```{r, fig.width=9, fig.height=9, code = readLines("01_getting_started/sales_analysis_challenge.R", encoding="UTF-8")}
```


# Data Acquisition

## YouTube API

The API call uses the public *YouTube Data API v3* with just an API-key
(without O-Auth). The 10 most popular videos in the US are fetched and
interesting information is selected.

```{r, code = readLines("02_data_wrangling/youtube_api.R", encoding="UTF-8")}
```

## Rose Scraping

To prevent the access to the www.rosebikes.de website with every website build,
the script has been split. The main part acquires the data and saves it to a file.
```{r, eval = FALSE, code = readLines("02_data_wrangling/rose_scrape.R", encoding="UTF-8")}
```

The second part reads the file and outputs 10 lines.
```{r}
read_rds("00_data/rose_bikes.rds") %>% head(n=10)
```

The complete data set contains 171 model / color variants with information about
the category, model, color, price, wheels, switchgear, chain, brakes and the
link.


# Data Wrangling

## Patent Dominance

The data *assignee* and *patent_assignee* have been loaded and converted to a
data.table. Then all duplicate assignments have been removed, so that one patent
only counts once. The tables were combined on the *assignee.id* and
*patent_assignee.assignee_id*.
An analysis resulting in the output of the 10 US companies with the most
patents has been conducted.
```{r, eval = FALSE, code = readLines("02_data_wrangling/patent_dominance.R", encoding="UTF-8")}
```
```{r}
read_rds("00_data/patents/analyzed/patent_dominance.rds")
```

## Patent Activity

```{r, eval = FALSE, code = readLines("02_data_wrangling/patent_activity.R", encoding="UTF-8")}
```
```{r}
read_rds("00_data/patents/analyzed/patent_activity.rds")
```

## Innovation in Tech

```{r, eval = FALSE, code = readLines("02_data_wrangling/patent_innovation.R", encoding="UTF-8")}
```
The solution only considering the sequence==0 class as the *main class*:
```{r}
read_rds("00_data/patents/analyzed/patent_innovation_0.rds")
```
The solution only considering all classes:
```{r}
read_rds("00_data/patents/analyzed/patent_innovation.rds")
```
