---
title: "Journal (reproducible report)"
author: "Julius Häuslein"
date: "2020-11-23"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    toc_depth: 3
    #code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```

# Bike Sales

```{r, fig.width=9, fig.height=9, code = readLines("01_getting_started/sales_analysis_challenge.R", encoding="UTF-8")}
```

# Data Acquisition

## Rose Scraping

To prevent the access to the www.rosebikes.de website with every website build,
the script has been split. The main part acquires the data and saves it to a file.
```{r, eval = FALSE, code = readLines("02_data_wrangling/rose_scrape.R", encoding="UTF-8")}
```

The second part reads the file and outputs 10 lines.
```{r}
  read_rds("00_data/rose_bikes.rds") %>% head(n=10)
```

The complete data set contains 171 model / color variants with information about
the category, model, color, price, wheels, switchgear, chain, brakes and the
link.